Systematic review of outbreak response models: data analysis

### 2023-04-23 analyses/scripts/orv_sys_rev_data_analysis_by_collab_type.Rmd
Changed output format to pdf
Removed redundant loaded packages

---
title: "Systematic review of outbreak response models: data analysis"
author: "James M. Azam, Xiaoxi Pang, Elisha B. Are, Juliet R.C. Pulliam, Matthew J. Ferrari"
date: today()
output:
  word_document:
    keep_md: yes
#  html_notebook
---

@@

```{r echo=FALSE, message=FALSE}
#' load packages
library('tidyverse')
library('readr')
library('ggthemes')
library('scales')
library('janitor')
library('forcats')
library('stringr')
library('countrycode')
library('bib2df')
library('conflicted')

>>>>

---
title: "Systematic review of outbreak response models: data analysis"
author: "James M. Azam, Xiaoxi Pang, Elisha B. Are, Juliet R.C. Pulliam, Matthew J. Ferrari"
date: today()
output:
  # word_document:
  #   keep_md: yes
#  html_notebook
  pdf_document:
    toc: yes
    keep_tex: yes
    fig_crop: no
---

@@

```{r echo=FALSE, message=FALSE}
#' load packages
library('tidyverse')
library('ggthemes')
library('scales')
library('janitor')
library('countrycode')
library('bib2df')
library('conflicted')
